New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/schur.tex
preuve 3.1 v3

We first examine the case where \(h(x) \leqslant k\). We assume \(h(x+y) \leqslant k\), otherwise we are fine. 
Thus by definition of \(h\), we have \(h(x) = f(p-u) = f(p-v) = h(y)\).
\begin{itemize}
\item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
We have \(f(p-u) = f(p-v)  \leqslant k\) and \(p-u + p-v > p\), the extra condition on \(f\) provides \(f(p-u-v) \neq f(p-u)\).
We assumed \(h(x+y) \leqslant k\) hence \(h(x+y) = f(p-u-v)\). Since \(h(x) = f(p-u)\), we have at last \(h(x+y) \neq h(x)\).
\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f((p-u + p-v))\). Since \(f(p-u+p-v) \neq f(p-u)\),
we get \(h(x+y) \neq h(x)\).
\end{itemize}

We now assume \(h(x) > k\). Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta\). 
We have the two same cases as before.

\begin{itemize}
\item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
We assume \(h(x+y) > k\) otherwise the expected result is trivial.
Since \(g(\alpha) = g(\beta)\), the sum-free condition garanties \(g\alpha) \neq g(\alpha+\beta)\), 
thus \(h(x+y) = k + g(\alpha + \beta) \neq k + g(\alpha) = h(x)\).
\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
Because of the assumption \(h(x) > k\), we necessarily have \(f(p-u) = k+1 = f(p-v)\). 
Then \(f(p-(u+v-p)) = f(p-u + p-v) \leqslant k \) with the sum-free condition on \(f\), 
hence \(h(x+y) = f(p-(u+v-p)) \) by construction of \(h\). Thus \(h(x+y) \leqslant k < h(x)\).
\end{itemize}

>>>>

We first examine the case where \(h(x) \leqslant k\). We assume \(h(x+y) \leqslant k\), otherwise we are fine. 
Thus by definition of \(h\), we have \(h(x) = f(p-u) = f(p-v) = h(y)\).
\begin{itemize}
\item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
We have \(f(p-u) = f(p-v)  \leqslant k\) and \(p-u + p-v > p\), the extra condition on \(f\) provides \(f(p-u-v) \neq f(p-u)\).
We assumed \(h(x+y) \leqslant k\) hence \(h(x+y) = f(p-u-v)\). Since \(h(x) = f(p-u)\), we have at last \(h(x+y) \neq h(x)\).
\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f(p-u + p-v)\). Since \(f(p-u+p-v) \neq f(p-u)\),
we get \(h(x+y) \neq h(x)\).
\end{itemize}

We now assume \(h(x) > k\). Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). 
We have the two same cases as before.

\begin{itemize}
\item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
We assume \(h(x+y) > k\) otherwise the expected result is trivial.
Since \(g(\alpha) = g(\beta)\), the sum-free condition garanties \(g(\alpha) \neq g(\alpha+\beta)\), 
thus \(h(x+y) = k + g(\alpha + \beta) \neq k + g(\alpha) = h(x)\).
\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
Because of the assumption \(h(x) > k\), we necessarily have \(f(p-u) = k+1 = f(p-v)\). 
Then \(f(p-(u+v-p)) = f(p-u + p-v) \leqslant k \) with the sum-free condition on \(f\), 
hence \(h(x+y) = f(p-(u+v-p)) \) by construction of \(h\). Thus \(h(x+y) \leqslant k < h(x)\).
\end{itemize}
